### 2018-07-19 paper/design.tex
WIP on design

This section presents the different parts of the system in detail.
We align the presentation of the system with the taxonomy of 
\textcite{RoutingSurveyAnonymousProtocols}.
They categorize anonymous communication protocols using the following 
categories:
\begin{description}
  \item[Network structure]
    This describes the characteristics of the anonymous relays, the connections 
    between them and the underlying topology.

  \item[Routing information]
    This describes the network information available to entities deciding on 
    the route of an anonymous connection.

  \item[Communication model]
    This describes the entities that make the routing decisions and how they 
    make these decisions.
\end{description}

We first describe Sphinxes, which is an adaptation of the Sphinx~\cite{Sphinx} 
mix-header format.
This affects very few parts of the taxonomy above.

>>>>

This section presents the different parts of the system in detail.
We align the presentation of the system with the taxonomy of 
\textcite{RoutingSurveyAnonymousProtocols}.
They categorize anonymous communication protocols using the following 
categories (see \cite[Table 1]{RoutingSurveyAnonymousProtocols}):
\begin{description}
  \item[Network structure]
    This describes the characteristics of the anonymous relays, the connections 
    between them and the underlying topology.
    The subcategories are
    \begin{enumerate*}
      \item network topology,
      \item connection type (direction, synchronization),
      \item symmetry (node roles, node topology for routing, decentralization).
    \end{enumerate*}

  \item[Routing information]
    This describes the network information available to entities deciding on 
    the route of an anonymous connection.
    The subcategories are
    \begin{enumerate*}
      \item network view necessary for making routing decisions,
      \item triggers for routing information updates.
    \end{enumerate*}

  \item[Communication model]
    This describes the entities that make the routing decisions and how they 
    make these decisions.
    The subcategories are
    \begin{enumerate*}
      \item routing type (who selects nodes per route),
      \item scheduling (traffic prioritization),
      \item node selection (determinism, selection set, selection probability).
    \end{enumerate*}

  \item[Performance]
    This describes things like latency and communication mode.
    The subcategories are
    \begin{enumerate*}
      \item protocol latency,
      \item communication mode (connection- or message-based).
    \end{enumerate*}
\end{description}

We first describe Sphinxes (\cref{Sphinxes}), which is an adaptation of the 
Sphinx~\cite{Sphinx} mix-header format.
This means that we inherit some properties from Sphinx and due to being only a 
header format, it only imposes some restrictions in the above categories.
Sphinxes provides, just as Sphinx, source-routed (communication model), 
unidirectional (network structure), message-based (performance) communication.
As such, it relies on a flat routing-topology (network structure) with fair 
scheduling (communication model) --- as all packets are indistinguishable they 
must be processed on a first-in-first-out basis.
Sphinxes also introduces some probability to the node selection, but this is 
only a probabilistic selection among already selected nodes and only 
interesting against passive adversaries (an active adversary can learn the 
entire set).

Sphinxes does \emph{not} introduce any restrictions on whether the network 
topology must be fully connected or not, be asynchronous (as in Tor) or 
synchronous (as in mix-nets), whether node selection must be uniformly random 
or not.
Just as Sphinx, it can be used in many different settings.

Next, we describe the \ac{SPOR} protocol (\cref{SPOR}).
